### 2024-08-08 paper.tex
mostly finished first case of jordan form

\subsection{The general case}
In the case where \(X\) was a single Jordan block, it was helpful to have the condition that all the nonzero \(a\)'s were to the right of all the nonzero \(b\)'s.
This allowed some tricks with right-shifting.
In the general case, the parameters \(a\) and \(b\) are not necessarily in such a helpful form.
We will see, however, that we can change basis of \(\mathbb{C}^m\) to put them in a nice form.
\par Recall our nilpotent operator \(A_{X, a, b}\) on \(\mathbb{C}^m \times \mathbb{C}^n\).
We can define a map \(\mathbb{C}^m \to \mathbb{C}\) by \(x \mapsto x \cdot a\).
Then, by the previous lemma, we can choose a Jordan basis \(e_{ij}\) of \(\mathbb{C}^m\) so that at most one \((i, j)\) has \(f(e_{ij}) \neq 0\).
This implies that there are some \(P, k, b'\) such that \(PA_{X, a, b}P^{-1} = A_{X, 1_k, b'}\).
So, without loss of generality, we may consider this case, where \(a = 1_k\).
\par Write our basis of \(\mathbb{C}^m\) as \(e_{ij}\) and our basis of \(\mathbb{C}^n\) as \(f_j\).
Let \(i_0, r\) be such that \(a = e_{i_0, \lambda_{i_0} - r + 1}\).
Let \(b' = A^{n + r} e_{i_0, \lambda_{i_0}} = b + e_{i_0, \lambda_{i_0} - r - n}\).
Let \(b_{ij}'\) be the projection of \(b'\) onto \(e_{ij}\).
For each \(i\), let \(p_i = \max\{j : b_{ij}' \neq 0\}\).
Then for each \(i \neq i_0\), let \(q_i = \lambda_i - p_i\).  Let \(q_{i_0} = \lambda_{i_0} - r - p_{i_0}\).
Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
Now, it will be more convenient to assume our indices are such that \(q_i\) is nonincreasing, so we will do that.
\par We have two cases, which will closely resemble the cases we had when \(X\) was a single Jordan block.
\subsubsection{First case: \(n + \max_i p_i \geq q_{i_0} + p_{i_0}\)}
We list the chains in (roughly) decreasing order.
First, for each \(i\) such that \(q_i \geq n + r\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
\par Now we handle \(e_{i_0, \lambda_{i_0}}\).
Let \(P = \max_{i : q_i < n + r} p_i\).
Set 
\[v = e_{i_0, \lambda_{i_0}} - (A^{r + n + P}e_{i_0, \lambda_{i_0}} >> r + n + P).\]
Note that \(A^{r + n} e_{i_0, \lambda_{i_0}} = b'\), so \(A^{r + n + P} e_{i_0, \lambda_{i_0}} = A^P b' = b' << P\).
Also note that if we shift \(b'\) left \(P\) times, we zero out all the rows \(i\) where \(q_i < n + r\).
This ensures that the operation of shifting \(b' << P\) right \(r + n + P\) times is invertible by applying \(A\), and thus shifting left, \(r + n + P\) times.
So, we take the chain of length \(r + n + P\) beginning with \(v\).
How do we know this is linearly independent from what came before?
Something to do with the condition on \(n\)...
\par Now, we handle the \(i\) with \(q_i < n + r\).
If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
Otherwise, we set 
\[v_i = A^{n + r - q_i} e_{i_0, \lambda_{i_0}} - \sum_{k = 1}^{p_i}b_{i,k} e_{i,k + q_i}.\]
Note that \(v_i\) is just

>>>>

\subsection{The general case}
In the case where \(X\) was a single Jordan block, it was helpful to have the condition that all the nonzero \(a\)'s were to the right of all the nonzero \(b\)'s.
This allowed some tricks with right-shifting.
In the general case, the parameters \(a\) and \(b\) are not necessarily in such a helpful form.
We will see, however, that we can change basis of \(\mathbb{C}^m\) to put them in a nice form.
\par Recall our nilpotent operator \(A_{X, a, b}\) on \(\mathbb{C}^m \times \mathbb{C}^n\).
We can define a map \(\mathbb{C}^m \to \mathbb{C}\) by \(x \mapsto x \cdot a\).
Then, by the previous lemma, we can choose a Jordan basis \(e_{ij}\) of \(\mathbb{C}^m\) so that at most one \((i, j)\) has \(f(e_{ij}) \neq 0\).
This implies that there are some \(P, k, b'\) such that \(PA_{X, a, b}P^{-1} = A_{X, 1_k, b'}\).
So, without loss of generality, we may consider this case, where \(a = 1_k\).
\par Write our basis of \(\mathbb{C}^m\) as \(e_{ij}\) and our basis of \(\mathbb{C}^n\) as \(f_j\).
Let \(i_0, r\) be such that \(a = e_{i_0, \lambda_{i_0} - r + 1}\).
Let \(b' = A^{n + r} e_{i_0, \lambda_{i_0}} = b + e_{i_0, \lambda_{i_0} - r - n}\).
Let \(b_{ij}'\) be the projection of \(b'\) onto \(e_{ij}\).
For each \(i\), let \(p_i = \max\{j : b_{ij}' \neq 0\}\).
Then for each \(i \neq i_0\), let \(q_i = \lambda_i - p_i\).  Let \(q_{i_0} = \lambda_{i_0} - r - p_{i_0}\).
Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
Now, it will be more convenient to assume our indices are such that \(q_i\) is nonincreasing, so we will do that.
\par We have two cases, which will closely resemble the cases we had when \(X\) was a single Jordan block.
\subsubsection{First case: \(n + \max_i p_i \geq q_{i_0} + p_{i_0}\)}
We list the chains in (roughly) decreasing order.
First, for each \(i\) such that \(q_i \geq n + r\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
\par Now we handle \(e_{i_0, \lambda_{i_0}}\).
Let \(P = \max_{i : q_i < n + r} p_i\).
Set 
\[v = e_{i_0, \lambda_{i_0}} - (A^{r + n + P}e_{i_0, \lambda_{i_0}} >> r + n + P).\]
Note that \(A^{r + n} e_{i_0, \lambda_{i_0}} = b'\), so \(A^{r + n + P} e_{i_0, \lambda_{i_0}} = A^P b' = b' << P\).
Also note that if we shift \(b'\) left \(P\) times, we zero out all the rows \(i\) where \(q_i < n + r\).
This ensures that the operation of shifting \(b' << P\) right \(r + n + P\) times is invertible by applying \(A\), and thus shifting left, \(r + n + P\) times.
So, we take the chain of length \(r + n + P\) beginning with \(v\).
How do we know this is linearly independent from what came before?
Something to do with the condition on \(n\)...
\par Now, we handle the \(i\) with \(q_i < n + r\).
If \(p_i \leq \max_{k > i} p_k\), then we take the chain beginning with \(e_{i,p_i + q_i}\) of length \(p_i + q_i\).
Otherwise, we set 
\[v_i = A^{n + r - q_i} e_{i_0, \lambda_{i_0}} - \sum_{k = 1}^{p_i}b_{i,k}' e_{i,k + q_i}.\]
Note that \(A^{q_i} v_i\) is just \(b'\) with row \(i\) zeroed out.
Then, \(A^{q_i + \max_{k > i} p_k} v_i\) will have, in addition, rows \(k\) zeroed out, for all \(k > i\).
This ensures that shifting \(A^{q_i + \max_{k > i} p_k} v_i\) right \(q_i + \max_{k > i} p_k\) times will be inverted by applying \(A\), and thus shifting left, \(q_i + \max_{k > i} p_k\) times.
So, we take the chain beginning with \(v_i - (A^{q_i + \max_{k > i} p_k} v_i >> q_i + \max_{k > i} p_i)\), which has length \(q_i + \max_{k > i} p_k\).
\par TODO: where did I use the fact that \(n + \max_i p_i \geq q_{i_0} + p_{i_0}\)?

\subsubsection{Second case: \(n + \max_i p_i \leq q_{i_0} + p_{i_0}\)}
